I put my finger on today as I am restarting the project and wanted to remind myself of the wearability. First as I type, my wrist  wrests awkwardly, this is due to the mounting point of the finger. Second blood circulation at my thumb and index finger are not great due to the mounting Velcro straps to hold the flex sensors. The sensors themselves dig into my skin at the finger tips and at the base. Most prominent is the digging in on the index finger. As I wear the device the compute strap has a wire under that digs in as well. 

The finger mounting point is awkward to type on a keyboard and the sensor mounting makes it awkward to type on a phone. Taking pictures of the hand is also difficult. 

I am also not pleased with the Velcro finger straps removing sensation on the finger tips (often the straps make contact with the grasped object first). I also am not a fan of the open wires (and more generally the bulk) of the compute module on the wrist. Note too that this is without batter which adds considerable weight. 

The finger itself is worn and would need considerable rework if I go that route. I advise we continue to use the current finger, but rethink the control electronics.



What is my budget for this? \$ 100 for version 1.2. + the a couple hundred for version 2?

I think we ought to make a new glove thing and rework the current compute module for version 1.2. The underlying hardware is probably fine for an early evaluation provided I fix the comfort issues. Version 2 should have a better scheme for mounting the finger. 